---
title: "Johannes Markus Feldhege's CV"
author: Johannes Markus Feldhege
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  english:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "./data/",  
  pdf_mode = params$pdf_mode,
  english = params$english
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


```{r}
if(params$pdf_mode){
  if(params$english){
      cat("View this CV online with links at https://www.johannesfeldhege.de/cv/")
  } else {
    cat("Sie finden diesen Lebenslauf online unter https://www.johannesfeldhege.de/cv/")
  }
} else {
    if(params$english){
        cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://www.johannesfeldhege.de/assets/CV_Johannes_Feldhege.pdf)")
    } else{
      cat("[<i class='fas fa-download'></i> Laden Sie ein pdf des Lebenslauf herunter](https://www.johannesfeldhege.de/assets/CV_Johannes_Feldhege.pdf)")
    }
}
```

`r if(params$english){"Contact"} else {"Kontakt"}` {#contact}
--------------------------------------------------------------------------------
```{r}
CV %>% print_contact_info()
```



`r if(params$english){"Programming Skills"} else {"Programmieren"}` {#skills}
--------------------------------------------------------------------------------

```{r}
#CV %>% print_skill_bars()
```
<i class="fab fa-r-project"></i> R 
<br> <i class="fa fa-area-chart" aria-hidden="true"></i> tidyverse
<br><i class="fab fa-markdown"></i> RMarkdown / Quarto
<br> <i class="fas fa-code-branch"></i> Git 
<br> <i class="fab fa-github"></i> GitHub
<br><i class="fab fa-html5"></i> HTML
<br><i class="fa fa-database"></i> SQL



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r disclaimer_en, echo = FALSE, results = 'asis', eval = params$english}
cat("Made with the R packages [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](https://github.com/nstrayer/datadrivencv). 

Source code: [github.com/jfeldhege/cv](https://github.com/jfeldhege/cv/).\n")

cat(glue::glue("<p>Last updated on {format(Sys.Date(), '%d.%m.%Y')}.</p>"))
```

```{r disclaimer_de, echo = FALSE, results = 'asis', eval = !params$english}
cat("Mit den R Paketen [**pagedown**](https://github.com/rstudio/pagedown) und [**datadrivencv**](https://github.com/nstrayer/datadrivencv) erstellt. 

Quellcode: [github.com/jfeldhege/cv](https://github.com/jfeldhege/cv/).")

cat(glue::glue("<p>Letzte Aktualisierung am {format(Sys.Date(), '%d.%m.%Y')}.</p>"))
```



Main
================================================================================

Johannes Markus Feldhege {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



`r if(params$english){"Education"} else{"Ausbildung"}` {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

`r if(params$english){"Professional Experience"} else{"Berufliche Erfahrung"}` {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('positions')
```


`r if(params$english){"Selected Publications"} else{"Ausgewählte Veröffentlichungen"}` {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```


`r if(params$english){"Conference Posters and Talks"} else{"Konferenzbeiträge"}`  {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('conferences')
```

`r if(params$english){"Conference Posters and Talks"} else{"Konferenzbeiträge"}`  {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('conferences')
```



`r if(params$english){"Projects"} else{"Projekte"}` {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('projects')
```


```{r}
CV %<>% print_links()
```

<br>
